XSFACE Analyses

### 2018-01-12 analysis-main/main_analyses_bll.Rmd
hope this works

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = TRUE)
options(error = browser)
```

```{r}
rm(list=ls())
library(readr)
library(plyr) # need to load this for scripts, always load before
library(dplyr)
library(tidyr)
library(langcog)
library(ggplot2)
library(lubridate)
```

@@

```{r}
d <- read_csv("../data/consolidated_data.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}

@@

# Namings and face detections

@@

```{r}
sb <- plyr::ddply(d,~subid, summarize.naming, window=c(-2,0)) ## used 2 second window as in ms draft
sa <- plyr::ddply(d,~subid, summarize.naming, window=c(0,2))

sb$window <- "before"
sa$window <- "after"
s <- rbind(sb,sa)
s$window <- factor(s$window)

# not used, commented out
# s$first.instance <- s$naming.instance == 1
# s$log.instance <- round(log10(s$naming.instance)*4)/4
# s$binned.instance <- 10^(round(log10(s$naming.instance)*4)/4)
# s$face.logical <- s$face != 0

## try plotting individuals
mss <- ddply(s,~subid+age.grp+window,summarise,
               face = mean(face, na.rm="TRUE"))
```

@@

```{r}
ms <- namings %>%
  group_by(age.grp, subid, naming.instance, familiarity, name) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp, naming.instance, familiarity) %>%
  multi_boot_standard(col = "face", na.rm = TRUE)
```

@@

## Now calculate face detection differences from base rate

```{r}

  n <- ddply(s,~subid+age.grp,summarise,
             face = mean(face, na.rm="TRUE"))

  n$br <- ddply(d,~subid+age.grp,summarise,
              face=mean(face, na.rm="TRUE"))$face

  n$br.diff <- n$face - n$br

#   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3)
  qplot(age.grp,br.diff,position=position_jitter(.2),
        data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") +
    scale_x_continuous(breaks=c(8,12,16)) +
    geom_abline(slope=0,intercept=0,lty=2) +
    stat_summary(fun.data="mean_cl_boot",color="red")
#   dev.off()
```

<!-- # CDIs, namings, and face detections -->

<!-- ```{r} -->
<!-- cdi_namings <- left_join(naming_rate, cdis) -->

<!-- qplot(comprehension, facets= .~ age.grp, data = cdi_namings) + -->
<!--   theme_bw() -->

<!-- qplot(production, facets= .~ age.grp, data = cdi_namings) + -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ## CDIs and namings -->

<!-- Just out of curiousity, are there any major differences in terms of CDIs by naming rate? (Would help to establish the validity of the naming rate analyses). -->

<!-- ```{r} -->
<!-- ggplot(cdi_namings, -->
<!--        aes(x = rate, y = comprehension)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE) + -->
<!--   facet_grid(.~age.grp) + -->
<!--   xlab("Namings per minute") + -->
<!--   ylab("CDI Summed Comprehension Vocabulary") + -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- cdis <- read_csv("../data/cdis/cdi_summary.csv") -->
<!-- left_join(naming_rate, cdis) %>% -->
<!--   ggplot(aes(x = rate, y = production)) + -->
<!--   geom_point() + -->
<!--   geom_smooth(method = "lm", se = FALSE) + -->
<!--   facet_grid(.~age.grp) + -->
<!--   xlab("Namings per minute") + -->
<!--   ylab("CDI Summed Production Vocabulary") + -->
<!--   theme_bw() -->
<!-- ``` -->

>>>>

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = TRUE)
options(error = browser)

```

```{r}
rm(list=ls())
library(readr)
library(langcog)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
```

@@

```{r}
d <- read_csv("../data/consolidated_data_3dets.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))
demo <- read_csv("../data/demographics/demographics.csv")
#cdis <- read_csv("../data/cdis/cdi_summary.csv") ## not in repo
```

@@

```{r}
#d$face=d$faceVJ
#d$face=d$faceMT
d$face=d$faceOP
#d$face=d$handOP

@@

<!-- # Namings and face detections -->

@@

```{r}
aroundNamings <- d %>%
  filter(!is.na(posture)) %>%
  group_by(subid) %>%
  do(summarize.naming(.))

ggplot(aroundNamings, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("detections within naming window") + 
  xlab("Age (months)") + 
  facet_grid(.~familiarity) +
  theme_bw()

```{r}
# mss <- d %>%
#   filter(!is.na(posture)) %>%
#   filter(!is.na(face)) %>%
#   group_by(age.grp, posture, subid) %>%
#   summarise(faceArea = mean(faceArea, na.rm="TRUE")) %>%
#   group_by(age.grp)
# 
# 
# sb_summary <- sb %>%
#   filter(!is.na(posture)) %>%
#   filter(!is.na(face)) %>%
#   group_by(age.grp, posture, subid) %>%
#   dplyr::summarise(face = count(face)) %>%
#   group_by(age.grp)
# 
# 
# nameFreq <- sb %>%
#   filter(!is.na(posture)) %>%
#   filter(!is.na(face)) %>%
#   group_by(age.grp, posture, subid) %>%
#   dplyr::summarise(nameFreq= max(naming.instance, na.rm="TRUE")) %>%
#   group_by(age.grp)
# 
# ggplot(nameFreq, aes(x = factor(age.grp), y = nameFreq, col = posture)) + 
#   geom_boxplot() + 
#   ylab("within window") + 
#   xlab("Age (months)") + 
#   theme_bw() 
# 
# 
# # ggplot(sb_summary, aes(x = factor(age.grp), y = face, col = posture)) + 
# #   geom_boxplot() + 
# #   ylab("within window") + 
# #   xlab("Age (months)") + 
# #   theme_bw()

sb <- sb %>%
  filter(!is.na(posture))

ggplot(sb, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("within window") + 
  xlab("Age (months)") + 
  facet_grid(.~familiarity) +
  theme_bw()

```

@@

```{r}
ms <- namings %>%
  dplyr::group_by(age.grp, subid, naming.instance, familiarity, name) %>%
  dplyr::summarise(face = mean(face)) %>%
  dplyr::group_by(age.grp, naming.instance, familiarity) %>%
  multi_boot_standard(col = "face", na.rm = TRUE)
```

@@

<!-- ## Now calculate face detection differences from base rate -->

<!-- ```{r} -->

<!--   n <- ddply(s,~subid+age.grp,summarise, -->
<!--              face = mean(face, na.rm="TRUE")) -->

<!--   n$br <- ddply(d,~subid+age.grp,summarise, -->
<!--               face=mean(face, na.rm="TRUE"))$face -->

<!--   n$br.diff <- n$face - n$br -->

<!-- #   pdf("~/Projects/xsface/writeup/figures/naming_faces_diff.pdf",width=4,height=3) -->
<!--   qplot(age.grp,br.diff,position=position_jitter(.2), -->
<!--         data=subset(n,age.grp>4),xlab="Age (Months)",ylab="Face detections relative to base rate") + -->
<!--     scale_x_continuous(breaks=c(8,12,16)) + -->
<!--     geom_abline(slope=0,intercept=0,lty=2) + -->
<!--     stat_summary(fun.data="mean_cl_boot",color="red") -->
<!-- #   dev.off() -->
<!-- ``` -->

<!-- <!-- # CDIs, namings, and face detections --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- cdi_namings <- left_join(naming_rate, cdis) --> -->

<!-- <!-- qplot(comprehension, facets= .~ age.grp, data = cdi_namings) + --> -->
<!-- <!--   theme_bw() --> -->

<!-- <!-- qplot(production, facets= .~ age.grp, data = cdi_namings) + --> -->
<!-- <!--   theme_bw() --> -->

<!-- <!-- ``` --> -->

<!-- <!-- ## CDIs and namings --> -->

<!-- <!-- Just out of curiousity, are there any major differences in terms of CDIs by naming rate? (Would help to establish the validity of the naming rate analyses). --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- ggplot(cdi_namings, --> -->
<!-- <!--        aes(x = rate, y = comprehension)) + --> -->
<!-- <!--   geom_point() + --> -->
<!-- <!--   geom_smooth(method = "lm", se = FALSE) + --> -->
<!-- <!--   facet_grid(.~age.grp) + --> -->
<!-- <!--   xlab("Namings per minute") + --> -->
<!-- <!--   ylab("CDI Summed Comprehension Vocabulary") + --> -->
<!-- <!--   theme_bw() --> -->
<!-- <!-- ``` --> -->

<!-- <!-- ```{r} --> -->
<!-- <!-- cdis <- read_csv("../data/cdis/cdi_summary.csv") --> -->
<!-- <!-- left_join(naming_rate, cdis) %>% --> -->
<!-- <!--   ggplot(aes(x = rate, y = production)) + --> -->
<!-- <!--   geom_point() + --> -->
<!-- <!--   geom_smooth(method = "lm", se = FALSE) + --> -->
<!-- <!--   facet_grid(.~age.grp) + --> -->
<!-- <!--   xlab("Namings per minute") + --> -->
<!-- <!--   ylab("CDI Summed Production Vocabulary") + --> -->
<!-- <!--   theme_bw() --> -->
<!-- <!-- ``` --> -->
